---
title: "Group 16 MLUL2 Assignment"
author: 
   - Anjali Rathore-12120089
   - Bhargavi Peddapati-12120067
   - Chiraag Kumar-12120055
   - Parmarth Matta-12120077
   - Raktim Srivastava-12120044
   
date: "10/09/2022"
output: pdf_document
---

# Install and Import Required Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
requiredPackages = c('Matrix','arules','arulesViz','recommenderlab','reshape2','RCurl')
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}
```

# Rules Mining – Association rules (Apriori algorithm)

The Apriori algorithm has three main measures namely support, confidence and lift. These three measures are used to decide the relative strength of the rules. In the model parameters, we set RHS to the chosen group and LHS refers to a frequent pattern that is observed.



- Support indicates how interesting a pattern is. In the algorithm configuration (params), We have set the threshold to 0.001 which means a pattern must have appeared at least 0.001 * nrow(tmp) = 18 times.

- Confidence value i.e 0.5 (set as a threshold in model params) means that in order to be included in the results, the rule has to be correct at least 50 percent of the time. This is particularly helpful to eliminate the unreliable rules.

- Lift indicates probability (support) of the itemset (pattern) over the product of the probabilities of all items in the itemset.



In general, high confidence and good lift are the standard measures to evaluate the importance of a particular rule/ association.

# Load Dataset

```{r cars}
#setwd("C:/Users/ADMIN/Desktop/data science/ISB/3_Term3/MLUSL2/Group Assignment")
terror_df <-read.csv("https://media.githubusercontent.com/media/Bhargavi-6/Group16_MLUL2_Assignment/main/terror_model_df.csv")
terror <- na.omit(terror_df)
head(terror_df)
dim(terror_df)
```

## Rename Group or Shorten lengthy group names


```{r pressure1, echo=TRUE}
terror_df$Group[terror_df$Group == "Kurdistan Workers' Party (PKK)"] <- "PKK"
terror_df$Group[terror_df$Group == "Al-Qaida in the Arabian Peninsula (AQAP)"] <- "AQAP"
terror_df$Group[terror_df$Group == "Houthi extremists (Ansar Allah)"] <- "Houthi_Extrm"
terror_df$Group[terror_df$Group == "Tehrik-i-Taliban Pakistan (TTP)"] <- "TTP"
terror_df$Group[terror_df$Group == "Al-Nusrah Front"] <- "Al-Nusrah"
terror_df$Group[terror_df$Group == "Islamic State of Iraq and the Levant (ISIL)"] <-"ISIL"
terror_df$Group[terror_df$Group == "Donetsk People's Republic"] <- "Donetsk_PR"
```

## Create 2 number of datasets

## Dataset #01 : Rules Mining

```{r pressure2, echo=TRUE}
terror_df_rules <- terror_df[1:6]
str(terror_df_rules)
head(terror_df_rules)
```

## Dataset #02 : Recommender System

```{r pressure3, echo=TRUE}
terror_df_recommender <- subset(terror_df,terror_df$Country == "India")
str(terror_df_recommender)
head(terror_df_recommender)
```

## Convert attributes to factor

```{r pressure4, echo=TRUE}
terror_df_rules[] <- lapply(terror_df_rules, factor)
str(terror_df_rules)
```

# Apriori model

## Islamic State (ISIL)

## Set rhs as Terror Group

```{r pressure5, echo=TRUE}
params <- list(support = 0.001, confidence = 0.3, minlen = 2)
group_ISIL <- list(rhs='Group=ISIL', default="lhs")

rules <- apriori(data = terror_df_rules, parameter= params, appearance = group_ISIL)
```

## Remove redundant rules if any

```{r pressure6, echo=TRUE}
rules <- rules[!is.redundant(rules)] 
```

## Top 5 patterns (ISIL) based on confidence

```{r pressure7, echo=TRUE}
subrules <- head(sort(rules, by="confidence"), 5)
inspect(head(subrules, 5))
```

## Network Graph

```{r pressure8, echo=TRUE}
plot(rules, method="graph", control=list(type="items"))
```

## Scatter Graph

```{r pressure9, echo=TRUE}
plot(rules, method="scatter", control=list(type="items"))
```
## Taliban

## Set rhs as Terror Group

```{r pressure10, echo=TRUE}
group_taliban <- list(rhs='Group=Taliban', default="lhs")
params <- list(support = 0.001, confidence = 0.3, minlen = 2)

rules <- apriori(data = terror_df_rules, parameter= params, appearance = group_taliban)
```

## Remove redundant rules if any

```{r pressure11, echo=TRUE}
rules <- rules[!is.redundant(rules)] 
```

#### Top 5 patterns (Taliban) based on confidence

```{r pressure12, echo=TRUE}
subrules <- head(sort(rules, by="confidence"), 5)
inspect(head(subrules, 5))
```

## Network Graph


```{r pressure13, echo=TRUE}
plot(rules, method="graph", control=list(type="items"))
```

## Scatter Plot

```{r pressure14, echo=TRUE}
plot(rules, method="scatter", control=list(type="items"))
```

## Boko Haram

## Set rhs as Terror Group


```{r pressure15, echo=TRUE}
group_boko_haram <- list(rhs='Group=Boko Haram', default="lhs")
params <- list(support = 0.001, confidence = 0.3, minlen = 2)
rules <- apriori(data = terror_df_rules, parameter= params, appearance = group_boko_haram)
```

## Remove redundant rules if any

```{r pressure16, echo=TRUE}
rules <- rules[!is.redundant(rules)] 
```

## Top 5 patterns (Boko Haram) based on confidence

```{r pressure17, echo=TRUE}
subrules <- head(sort(rules, by="confidence"), 5)
inspect(head(subrules, 5))
```

## Network Graph

```{r pressure18, echo=TRUE}
plot(rules, method="graph", control=list(type="items"))
```

## Scatter Graph

```{r pressure19, echo=TRUE}
plot(rules, method="scatter", control=list(type="items"))
```

# Recommendation System Across India

## Recommendation System of Terrorist Group and City

## covert to matrix format


```{r pressure20, echo=TRUE}
kill_matrix <- as.matrix(acast(terror_df_recommender, Group~city, value.var="nkill", fun.aggregate = mean))

dim(kill_matrix)
```

## recommendarlab realRatingMatrix format

```{r pressure21, echo=TRUE}
R <- as(kill_matrix, "realRatingMatrix")
```

## User-based collaborative filtering

```{r pressure22, echo=TRUE}
rec1 = Recommender(R, method="UBCF") 
```

## Item-based collaborative filtering

```{r pressure23, echo=TRUE}
rec2 = Recommender(R, method="IBCF") 

```

## SVD, POPULAR

```{r pressure24, echo=TRUE}
rec3 = Recommender(R, method="SVD")
rec4 = Recommender(R, method="POPULAR")
```


## create n recommendations for a Terrorist group

```{r pressure26, echo=TRUE}
group_name = "Sikh Extremists" 
result <- subset(terror_df_recommender, terror_df_recommender$Group==group_name)
head(result)
dim(result)
print(paste("The most at risk city from this Terrorist group : ",group_name))
prediction <- predict(rec1, R[group_name], n=3) 
as(prediction, "list")
prediction <- predict(rec2, R[group_name], n=3) 
as(prediction, "list")
prediction <- predict(rec3, R[group_name], n=3) 
as(prediction, "list")
prediction <- predict(rec4, R[group_name], n=3) 
as(prediction, "list")
```

## Recommendation System of City and Attack Type

## covert to matrix format

```{r pressure27, echo=TRUE}
attack_kill_matrix <- as.matrix(acast(terror_df_recommender, city~AttackType, value.var="nkill", fun.aggregate = mean))

dim(attack_kill_matrix)
```

## recommendarlab realRatingMatrix format

```{r pressure28, echo=TRUE}
R_attack <- as(attack_kill_matrix, "realRatingMatrix")
```

## User-based collaborative filtering

```{r pressure29, echo=TRUE}
rec1_attack = Recommender(R_attack, method="UBCF")
```

## Item-based collaborative filtering

```{r pressure30, echo=TRUE}
rec2_attack = Recommender(R_attack, method="IBCF")
```

## SVD, POPULAR

```{r pressure31, echo=TRUE}
#rec3_attack = Recommender(R_attack, method="SVD")
rec4_attack = Recommender(R_attack, method="POPULAR")
```


## create n recommendations for a Terrorist group

```{r pressure33, echo=TRUE}
city = "Bombay" 
result <- subset(terror_df_recommender, terror_df_recommender$city==city)
head(result)
dim(result)
print(paste("The attack type anticipated in the city : ",city))
prediction <- predict(rec1_attack, R_attack[city], n=3) 
as(prediction, "list")
prediction <- predict(rec2_attack, R_attack[city], n=3) 
as(prediction, "list")
#prediction <- predict(rec3_attack, R_attack[city], n=3) 
#as(prediction, "list")
prediction <- predict(rec4_attack, R_attack[city], n=3) 
as(prediction, "list")
```

## Recommendation System of City and Target Type

## covert to matrix format

```{r pressure34, echo=TRUE}
kill_matrix <- as.matrix(acast(terror_df_recommender, city~Target_type, value.var="nkill", fun.aggregate = mean))

dim(kill_matrix)
```

## recommendarlab realRatingMatrix format

```{r pressure35, echo=TRUE}
R <- as(kill_matrix, "realRatingMatrix")
```

## User-based collaborative filtering

```{r pressure36, echo=TRUE}
rec1 = Recommender(R, method="UBCF")
```

## Item-based collaborative filtering

```{r pressure37, echo=TRUE}
rec2 = Recommender(R, method="IBCF") 
```

## SVD, POPULAR

```{r pressure38, echo=TRUE}
#rec3 = Recommender(R, method="SVD")
rec4 = Recommender(R, method="POPULAR")
```

## create n recommendations for a Terrorist group

```{r pressure40, echo=TRUE}
city = "Bombay" 
result <- subset(terror_df_recommender, terror_df_recommender$city==city)
head(result)
dim(result)
print(paste("The target type anticipated in the city : ",city))
prediction <- predict(rec1, R[city], n=3) 
as(prediction, "list")
prediction <- predict(rec2, R[city], n=3) 
as(prediction, "list")
#prediction <- predict(rec3, R[city], n=3) 
#as(prediction, "list")
prediction <- predict(rec4, R[city], n=3) 
as(prediction, "list")
```


